---
title: "European-Union-States"
subtitle: "App-Pitch"
author: "Prafful Agrawal"
date: "July 31, 2020"
output: 
  ioslides_presentation:
     smaller: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
```

## Introduction

- In this project, we have developed a *shiny* application which can be used for exploring the different **European Union States**.

- The details regarding the EU states was *scraped off* the web. (from *[wikipedia](https://en.wikipedia.org/wiki/European_Union)*)

- The application presents the final output in *three* forms:

    1. **Summary** - key details for all the states.
    2. **State Details** - detailed information about a *single* state with an option to choose the state from a list.
    3. **Plots** - geographical plots for the EU states w.r.t. different variables, such as population, area and population density.
    
- Options have been given to *show/hide* various components of the application as desired. 

## 1. Summary

- In *summary*, we present some key details regarding all the states of the European Union which are presented in the form of a table.

- The details included are:

    1. **State** - name of the EU state.
    2. **Code** - *three* character ISO ALPHA-3 country code.
    3. **Capital** - name of the capital.
    4. **Further_Reading** - external link (to *wikipedia*) to continue reading.

## 2. State Details

- In *state details*, we present detailed information regarding a *single* state of the European Union.

- An option is provided to choose the member state to show details about.

- The details included are:

    1. **Flag** - flag of the EU state.
    2. **State** - name of the EU state.
    3. **Code** - *three* character ISO ALPHA-3 country code.
    4. **Capital** - name of the capital.
    5. **Location** - *latitude* and *longitude* information.
    6. **Population** - population in *Millions*. [as on January 01, 2020]
    7. **Area** - land area in *Thousand kilometer square*.
    8. **Population Density** - population density in *per kilometer square*.
    9. **Further_Reading** - external link (to *wikipedia*) to continue reading.

## 3. Plots

- In *plots*, we present geographical plots for the EU states w.r.t. *three* variables:

    1. **Population**
    2. **Area**, and
    3. **Population Density**.

- An option is provided to choose the plot(s) to display.

- An example plot is shown below:

```{r plot_example, results='asis', cache=TRUE}
# Import package
library(googleVis)

# Import data
eu_df <- read.csv("eu_states.csv")

# Initialize plot
plt <- gvisGeoChart(data = eu_df,
                    locationvar = "State",
                    colorvar = "Area",
                    options = list(height = "250",
                                   width = "750",
                                   region = "150")
)

# Show plot
print(plt, "chart")
```